Convective heat transport in stratified atmospheres at low and high Mach number

### 2016-10-28 tex/nusselt_paper.tex
improvements throughout

\begin{figure}[t]
\includegraphics[width=3.4375in]{./figs/ma_v_eps.png}
\caption{The maximum value of Ma which has been horizontally averaged and time averaged for $\geq 100 t_b$, 
beginning roughly $50t_b$ after
the start of simulations.  (a) For $\epsilon \leq 0.1$,
a scaling of $\text{Ma }\propto \{\epsilon^{0.50}, \epsilon^{0.51}\}$ 
at $\text{Ra }= \{10^2, 10^5\}$ exists.
When $\epsilon \rightarrow m_{ad}$, large deviations from this power law are seen.  
(b) At high $\epsilon$, Ma scales as Ra$^{0.28}$ until it reaches the supersonic regime, at which point it
follows a power law of Ra$^{-0.10}$.  At low $\epsilon$, consistent power laws are achieved throughout all
values of Ra studied, where $\text{Ma }\propto \{\text{Ra}^{0.26},\,\text{Ra}^{0.22}\}$
for $\epsilon = \{10^{-4}, 10^{-7}\}$. \textbf{All
error bars are negligible.}  \label{fig:ma_v_eps} }
\end{figure}

The Fully Compressible Navier-Stokes equations,
\begin{align}
&\begin{aligned}
&\frac{\partial \ln\rho}{\partial t} + \Div{\bm{u}} = -\bm{u}\cdot\grad\rho,
	\label{eqn:continuity_eqn}
\end{aligned}\\
&\begin{aligned}
\frac{\partial\bm{u}}{\partial t} + \grad T - &\nu\Div{\lilstressT} - \lilstressT\cdot\grad\nu = \\
&-\bm{u}\cdot\grad\bm{u} - T\grad\ln\rho + \bm{g} + \nu\lilstressT\cdot\grad\ln\rho,
\label{eqn:momentum_eqn}
\end{aligned}\\
&\begin{aligned}
\frac{\partial T}{\partial t} -\frac{1}{c_V}\left(\right.\chi&\left.\grad^2 T + \grad T\cdot\grad\chi\right) = \\
	&-\bm{u}\cdot\grad T - (\gamma-1)T\Div{\bm{u}} \\
	&+ \frac{1}{c_V}\left(\chi\grad T \cdot\grad\ln\rho +\nu\left[\lilstressT\cdot\nabla\right]\cdot\bm{u}\right), 
	\label{eqn:energy_eqn}
\end{aligned}
\end{align}
are evolved with a viscous stress tensor defined as
\begin{equation}
\sigma_{ij} \equiv \left(\frac{\partial u_i}{\partial x_j} + \frac{\partial u_j}{\partial x_i} - \frac{2}{3}\delta_{ij}\Div{\bm{u}}\right).
	\label{eqn:stress_tensor}
\end{equation}
These equations carry a total convective flux of the form
%\begin{equation}
$
\bm{F}_{\text{conv}} \equiv \bm{F}_{\text{enth}} + \bm{F}_{\text{KE}} + \bm{F}_{\text{PE}} + \bm{F}_{\text{visc}}.
$
%\end{equation}
Contributions from the enthalpy flux, $\bm{F}_{\text{enth}} \equiv \rho\bm{u}(c_V T + P/\rho)$;
the kinetic energy flux, $\bm{F}_{\text{KE}} \equiv \rho|\bm{u}|^2\bm{u}/2$;
the potential energy flux, $\bm{F}_{\text{PE}} \equiv \rho\bm{u}\phi$ (with $\phi \equiv -gz$);
and the viscous flux, $\bm{F}_{\text{visc}} \equiv -\rho\nu\bm{u}\cdot\lilstressT$, must all be considered. 
%Taking an inner product of
%Eq. \ref{eqn:momentum_eqn} with $\bm{u}$ and adding it to 
%Eq. \ref{eqn:energy_eqn}, the full energy equation in conservation form is retrieved,
%\begin{equation}
%\frac{\partial}{\partial t}\left(\rho\left[\frac{|\bm{u}|^2}{2} + c_V T + \phi\right]\right) +
%\Div{\bm{F}_{\text{conv}} + \bm{F}_{\text{cond}}} = 0,
%	\label{eqn:energy_eqn_full}
%\end{equation}
%where $\bm{F}_{\text{cond}} = -\kappa \grad T$.  
Understanding these flux terms and how they interact with the conductive flux, 
$\bm{F}_{\text{cond}} = -\kappa \grad T$, is crucial in characterizing
convective heat transport.

@@

The efficiency of convection is quantified by the Nusselt number.  
Nu is well-defined in RB convection
as total flux normalized by the steady-state background conductive flux 
\cite{johnston&doering2009, otero&all2002}.
In stratified convection Nu is more difficulut to define, but one of the earliest definitions used
was \cite{graham1975,hurlburt&all1984}
\begin{equation}
\text{Nu} \equiv \frac{F_{\text{conv, z}} + F_{\text{cond, z}} - F_{\text{A}}}{F_{\text{ref}} - F_{\text{A}}},
\label{eqn:nusselt}
\end{equation}
where $F_{\text{conv, z}}$ and $F_{\text{cond, z}}$ are the z-components of $\bm{F}_{\text{conv}}$ and $\bm{F}_{\text{cond}}$,
respectively.  $F_{\text{A}} \equiv -\kappa \partial_z T_{\text{ad}}$ is the adiabatic conductive flux, and
$\partial_z T_{\text{ad}} \equiv - g / c_{P}$ for an ideal gas in hydrostatic equilibrium.
$F_{\text{ref}} \equiv \Delta T / L_z$, where $\Delta T \equiv T(L_z) - T(0)$ is the 
conductive flux of a linear profile connecting the upper
and lower plates, which is constant for the choice of fixed-temperature boundaries.

We contend that this is the general form of the Nusselt number and illustrate this with a few limiting
cases. Convection works to
suppress entropy stratification and create isentropic atmospheres.  Under the Boussinesq approximation,
in which density variations are ignored, entropy stratification is directly proportional to temperature stratification,
such that $\grad S \rightarrow 0$ when $\grad T \rightarrow 0$.  Thus, for RB convection, the familiar Nu is
retrieved from Eq. \ref{eqn:nusselt} because $\grad T_{\text{ad}} = 0$.  
In the case of polytropic convection,
as $\epsilon \rightarrow m_{ad} + 1$, $g \rightarrow 0$, so
$\grad T_{\text{ad}} \rightarrow 0$.  In such a case, $F_{\text{A}} \rightarrow 0$ and the
definition of the RB Nu is appropriate to use, as convection carries all of the
flux \cite{brandenburg&all2005}. As $\epsilon \rightarrow 0$, 
$\grad T_{\text{ad}}\rightarrow \grad T_0$, and increasingly
smaller velocity and thermodynamic perturbations are needed to achieve $\grad S = 0$ (Fig. \ref{fig:ma_v_eps}a).
Here, the removal of $F_{\text{A}}$ in the numerator and denominator of Eq. \ref{eqn:nusselt} makes them both
O($\epsilon$), so the overall Nu is sensible.

@@

\textbf{Initial value problems were solved in which $T_1$ experienced an infinitesimal kick compared to $\epsilon$
away from hydrostatic and thermal equilibrium}.
Solutions were time-evolved until a long average of Nu showed little
dependence on depth. \textbf{A linear stability analysis determined that} the onset of convection
occurs at $\text{Ra}_c = \{10.06, 10.97, 10.97\}$ for $\epsilon = \{0.5, 10^{-4}, 10^{-7}\}$, respectively.  Rayleigh
numbers from values at onset up to nearly $10^6$Ra$_c$ for $\epsilon = 0.5$, $10^5$Ra$_c$ for $\epsilon = 10^{-4}$,
and $10^3$Ra$_c$ for $\epsilon = 10^{-7}$ were studied.

At large $\epsilon$ (0.5), shock systems form in the upper atmosphere near downflow lanes 
(Fig. \ref{fig:entropy_snapshots}a) and propagate toward upflow lanes.  
Such systems were reported in
both two \cite{cattaneo&all1990} and three \cite{malagoli&all1990} dimensional polytropic simulations previously.
These shocks heat material entering the downflows, reducing both the
buoyant driving and the efficiency of convective transport.

Low Mach number flows, such as those in an $\epsilon = 10^{-4}$ atmosphere (Fig. \ref{fig:entropy_snapshots}b)
have similar bulk thermodynamic structure but lack the complicating dynamics of shock heating. 
Low Ma flows are in pressure equilibrium with their suroundings, so
pressure forces are unlikely to be the sole cause of symmetry breaking in up- and downflows, as has been suggested
\cite{hurlburt&all1984};  it is more likely that these flows are responding to 
the effects of density stratification.
As Ra is increased to large values (Fig. \ref{fig:entropy_snapshots}c), thermodynamic structures 
no longer span the whole domain but rather break up into small packets which traverse the domain multiple
times before diffusing.  
The complicated nature of high Ra dynamics, especially in the low Ma regime,
has prevented the convergence of solutions in the regime of 
$\text{Ra }> 10^5\text{Ra}_c$ at low $\epsilon$.

\begin{figure}[t]
\includegraphics[width=3.4375in]{./figs/fluxes_fig.png}
\caption{Time-averaged flux profiles for high (top) and low (bottom) Ma flows at $\text{Ra }= 10^6$.  
The dashed lines correspond to the
enthalpy flux (orange, positive) and kinetic energy flux (purple, negative).  The grey dash-dot line is the
viscous flux, the blue dash-dot-dot line is the potential energy flux, 
and the green dotted line is the radiative flux with the adiabatic radiative flux removed. All
fluxes are normalized by $F_{\text{ref}} - F_{\text{A}}$, as in Eq. \ref{eqn:nusselt}.  The solid black line is
Nu, the properly normalized sum of all the fluxes \label{fig:flux_profiles} }
\end{figure}

At large Ra, the heat transport properties of the systems become increasingly complex and time-dependent.
Large $\epsilon$ flows exhibit two local maxima in the enthalpy flux and kinetic energy flux: one in the upper 
atmosphere caused by the shocks, and one in the lower atmosphere caused by the deep mixing of convective motions
(Fig. \ref{fig:flux_profiles}a).
At low $\epsilon$, only the deep maximum is present (Fig. \ref{fig:flux_profiles}b).  
Fixed-temperature boundary conditions allow the flux at the boundaries to vary, so many runs at $\text{Ra }> 10^5$
and $\epsilon = 10^{-4}$ exhibit states in which the flux entering the system at the bottom of the atmosphere 
exceeds that which leaves at the top.  
These states are punctuated by states of vigorous shearing, similar to those previously
reported in two-dimensional RB convection \cite{goluskin&all2014}.  These shearing states push the bottom temperature
gradient towards adiabatic, allowing the excess energy to exit through the upper boundary.  These shearing
states will be covered in more detail in a future paper.  Regardless, a proper long-term average over shearing
and non-shearing states retrieves an invariant flux (and Nu) profile throughout the depth
of the atmosphere.

\textbf{After appropriately time-averaging the fluxes,} a sensible Nu is retrieved.  Nusselt numbers for
all simulations at low and high Ma are plotted in Fig. \ref{fig:nu_v_ra}.  At $\epsilon = \{10^{-4}, 10^{-7}\}$,
scaling laws of $Nu \propto Nu^{\{0.31, 0.31\}}$ are retrieved.  At $\epsilon = 0.5$, in the near-sonic
regime ($Ra \leq 10^4$), the scaling of $Nu$ with $Ra$ is inflated, with $Nu \propto Ra^{0.45}$.  As simulations
pass into the supersonic regime and shocks start to form near the downflows,
that scaling drops to $Nu \propto Ra^{0.19}$.  Error on all power law scalings is negligible.

\begin{figure}[t]
\includegraphics[width=3.4375in]{./figs/nu_v_ra.png}
\caption{Variation of Nu as Ra increases at low and high Ma. 
At high $\epsilon$, a clear transition from the subsonic to supersonic regime is evident in the scaling
of Nu with Ra.  In the low $\epsilon$ regime, Nu scalings collapse onto a similar line which is
\textbf{reminiscent} of RB scalings \cite{johnston&doering2009}.  Error bars represent the square root of
the variance of Nu with depth. \textbf{Identify power law fits on plot, add 2/7 law?}
\label{fig:nu_v_ra} }
\end{figure}

@@

\subsection{acknowledgements}
This work was supported by the CU/NSO George Ellery Hale Graduate Fellowship
and supported by NASA LWS grant number NNX16AC92G.  Computations were conducted 
with support by the NASA High End Computing (HEC) Program through the NASA 
Advanced Supercomputing (NAS) Division at Ames Research Center
with allocations (GID s1647, PI Brown; GID g26133, PI Toomre).
We thank Axel Brandenburg, Mark Rast, and Jeff Oishi for many useful discussions.

>>>>

\begin{figure}[t]
\includegraphics[width=3.4375in]{./figs/ma_v_eps.png}
\caption{The maximum value of Ma which has been horizontally averaged and time averaged for $\geq 100 t_b$, 
beginning roughly $50t_b$ after
the start of simulations.  This time average is long enough that the profile is well converged
and error bars are negligible. (a) For $\epsilon \leq 0.1$,
a scaling of $\text{Ma }\propto \{\epsilon^{0.50}, \epsilon^{0.51}\}$ 
at $\text{Ra }= \{10^2, 10^5\}$ exists.
When $\epsilon \rightarrow m_{ad}$, large deviations from this power law are seen.  
(b) At high $\epsilon$, Ma scales as Ra$^{0.28}$ until it reaches the supersonic regime, at which point it
follows a power law of Ra$^{-0.10}$.  At low $\epsilon$, consistent power laws are achieved throughout all
values of Ra studied, where $\text{Ma }\propto \{\text{Ra}^{0.26},\,\text{Ra}^{0.22}\}$
for $\epsilon = \{10^{-4}, 10^{-7}\}$. 
\label{fig:ma_v_eps} }
\end{figure}

The Fully Compressible Navier-Stokes equations,
\begin{align}
&\begin{aligned}
&\frac{\partial \ln\rho}{\partial t} + \Div{\bm{u}} = -\bm{u}\cdot\grad\rho,
	\label{eqn:continuity_eqn}
\end{aligned}\\
&\begin{aligned}
\frac{\partial\bm{u}}{\partial t} + \grad T - &\nu\Div{\lilstressT} - \lilstressT\cdot\grad\nu = \\
&-\bm{u}\cdot\grad\bm{u} - T\grad\ln\rho + \bm{g} + \nu\lilstressT\cdot\grad\ln\rho,
\label{eqn:momentum_eqn}
\end{aligned}\\
&\begin{aligned}
\frac{\partial T}{\partial t} -\frac{1}{c_V}\left(\right.\chi&\left.\grad^2 T + \grad T\cdot\grad\chi\right) = \\
	&-\bm{u}\cdot\grad T - (\gamma-1)T\Div{\bm{u}} \\
	&+ \frac{1}{c_V}\left(\chi\grad T \cdot\grad\ln\rho +\nu\left[\lilstressT\cdot\nabla\right]\cdot\bm{u}\right), 
	\label{eqn:energy_eqn}
\end{aligned}
\end{align}
are evolved with a viscous stress tensor defined as
\begin{equation}
\sigma_{ij} \equiv \left(\frac{\partial u_i}{\partial x_j} + \frac{\partial u_j}{\partial x_i} - \frac{2}{3}\delta_{ij}\Div{\bm{u}}\right).
	\label{eqn:stress_tensor}
\end{equation}

Taking an inner product of
Eq. \ref{eqn:momentum_eqn} with $\bm{u}$ and adding it to 
Eq. \ref{eqn:energy_eqn} reveals the full energy equation,
\begin{equation}
\frac{\partial}{\partial t}\left(\rho\left[\frac{|\bm{u}|^2}{2} + c_V T + \phi\right]\right) +
\Div{\bm{F}_{\text{conv}} + \bm{F}_{\text{cond}}} = 0.
	\label{eqn:energy_eqn_full}
\end{equation}
The convective flux is
$
\bm{F}_{\text{conv}} \equiv \bm{F}_{\text{enth}} + \bm{F}_{\text{KE}} + \bm{F}_{\text{PE}} + \bm{F}_{\text{visc}}.
$
Contributions from the enthalpy flux, $\bm{F}_{\text{enth}} \equiv \rho\bm{u}(c_V T + P/\rho)$;
the kinetic energy flux, $\bm{F}_{\text{KE}} \equiv \rho|\bm{u}|^2\bm{u}/2$;
the potential energy flux, $\bm{F}_{\text{PE}} \equiv \rho\bm{u}\phi$ (with $\phi \equiv -gz$);
and the viscous flux, $\bm{F}_{\text{visc}} \equiv -\rho\nu\bm{u}\cdot\lilstressT$, must all be considered. 
%where $\bm{F}_{\text{cond}} = -\kappa \grad T$.  
Understanding these flux terms and how they interact with the conductive flux, 
$\bm{F}_{\text{cond}} = -\kappa \grad T$, is crucial in characterizing
convective heat transport.

@@

The efficiency of convection is quantified by the Nusselt number.  
Nu is well-defined in RB convection
as the total flux normalized by the steady-stateconductive flux 
\cite{johnston&doering2009, otero&all2002}.
In stratified convection Nu is more difficult to define, but one of the earliest definitions used
was \cite{graham1975,hurlburt&all1984}
\begin{equation}
\text{Nu} \equiv \frac{F_{\text{conv, z}} + F_{\text{cond, z}} - F_{\text{A}}}{F_{\text{ref}} - F_{\text{A}}},
\label{eqn:nusselt}
\end{equation}
where $F_{\text{conv, z}}$ and $F_{\text{cond, z}}$ are the z-components of $\bm{F}_{\text{conv}}$ and $\bm{F}_{\text{cond}}$,
respectively.  $F_{\text{A}} \equiv -\kappa \partial_z T_{\text{ad}}$ is the adiabatic conductive flux and
$\partial_z T_{\text{ad}} \equiv - g / c_{P}$ for an ideal gas in hydrostatic equilibrium.
$F_{\text{ref}} \equiv \Delta T / L_z$, where $\Delta T \equiv T(L_z) - T(0)$, is the 
conductive flux of a linear profile connecting the upper
and lower plates, which is constant for the choice of fixed-temperature boundaries.

We contend that this is the general form of the Nusselt number and illustrate this with a few limiting
cases. Convection eliminates
entropy stratification.  Under the Boussinesq approximation,
in which density variations are ignored, entropy stratification is directly proportional to temperature stratification
such that $\grad S \rightarrow 0$ when $\grad T \rightarrow 0$.  The familiar Nu in the RB problem is
therefore retrieved from Eq. \ref{eqn:nusselt} because $\grad T_{\text{ad}} = 0$.  
In the case of polytropic convection,  $g \rightarrow 0$
as $\epsilon \rightarrow m_{ad} + 1$.
In this limit, $F_{\text{A}} \rightarrow 0$ and the
definition of the RB Nu is appropriate to use, as convection carries all of the
flux \cite{brandenburg&all2005}. 
However, as $\epsilon \rightarrow 0$, 
$\grad T_{\text{ad}}\rightarrow \grad T_0$ and increasingly
smaller velocity and thermodynamic perturbations are needed to achieve $\grad S = 0$ (Fig. \ref{fig:ma_v_eps}a).
These perturbations carry what little flux exists in excess of the adiabatic, so the removal of 
$F_{\text{A}}$ in the numerator and denominator of Eq. \ref{eqn:nusselt} is essential for a reasonable Nu measurement.

@@

Initial value problems were solved in which $T_1$ 
was filled with infinitesimal, random noise compared to $T_0$ and $\epsilon$.
Solutions were time-evolved until a long average of Nu showed little
variance with depth. By performing a linear stability analysis, we determined that the onset of convection
occurs at $\text{Ra}_c = \{10.06, 10.97, 10.97\}$ for $\epsilon = \{0.5, 10^{-4}, 10^{-7}\}$, respectively.  
We studied Rayleigh
numbers from values at onset up to nearly $10^6$Ra$_c$ for $\epsilon = 0.5$, $10^5$Ra$_c$ for $\epsilon = 10^{-4}$,
and $10^3$Ra$_c$ for $\epsilon = 10^{-7}$.

At large Ma ($\epsilon = 0.5$), shock systems form in the upper atmosphere near downflow lanes 
(Fig. \ref{fig:entropy_snapshots}a) and propagate toward upflow lanes.  
Such systems were reported in
both two \cite{cattaneo&all1990} and three \cite{malagoli&all1990} dimensional polytropic simulations previously.
These shocks heat material entering the downflows, affecting the dynamics and heat transport
of these systems.

Low Ma flows ($\epsilon = 10^{-4}$)
have similar bulk thermodynamic structures (Fig. \ref{fig:entropy_snapshots}b).
As Ra is increased to large values (Fig. \ref{fig:entropy_snapshots}c), thermodynamic structures 
no longer span the whole domain but rather break up into small packets which traverse the domain multiple
times before diffusing.  
While it has been suggested that pressure forces cause symmetry breaking in up- and downflows,
\cite{hurlburt&all1984}, this effect seems to be secondary to flows obeying mass conservation as they traverse
the stratified medium.  We observe low Ma cases where the double-roll systems such as those in
Fig. \ref{fig:entropy_snapshots}b contain one roll of increased pressure and one roll of decreased pressure
where the up- and downflows bound these regions of pressure disequilibrium.

\begin{figure}[t]
\includegraphics[width=3.4375in]{./figs/fluxes_fig.png}
\caption{Time-averaged flux profiles for high (a) and low (b) Ma flows at $\text{Ra }= 10^6$.  
The dashed lines correspond to the
enthalpy flux (orange, positive) and kinetic energy flux (purple, negative).  The grey dash-dot line is the
viscous flux, the blue dash-dot-dot line is the potential energy flux, 
and the green dotted line is the radiative flux with the adiabatic radiative flux removed. Viscous and
potential energy fluxes are negligible in (a) and are not shown.  All
fluxes are normalized by $F_{\text{ref}} - F_{\text{A}}$, as in Eq. \ref{eqn:nusselt}.  The solid black line is
Nu, the properly normalized sum of all the fluxes \label{fig:flux_profiles} }
\end{figure}

%At large Ra, the heat transport properties of the systems become increasingly complex and time-dependent.
at large values of Ra in which shocks form, high Ma flows exhibit two 
local maxima in the enthalpy flux and kinetic energy flux (Fig. \ref{fig:flux_profiles}a).
Shock-heated fluid parcels sometimes spin-up as they are pushed into the lower atmosphere, creating deep,
rapidly-rotating regions
of mixing which persist for many overturn times.  These ``spinners'' sit inside of larger rolls created by their
neighboring up- and downflows and greatly influence the dynamics.
At low Ma, only the deep maximum is present (Fig. \ref{fig:flux_profiles}b).  
Fixed-temperature boundary conditions allow the flux at the boundaries to vary, so many runs at $\text{Ra }> 10^5$
and $\epsilon = 10^{-4}$ exhibit states in which the flux entering the system at the bottom of the atmosphere 
exceeds that which leaves at the top.  
These states are punctuated by states of vigorous shearing, similar to those previously
reported in two-dimensional RB convection \cite{goluskin&all2014}.  
These shearing states push the bottom temperature
gradient towards adiabatic, allowing the excess energy to exit through the upper boundary.  These shearing
states will be covered in more detail in a future paper.  Regardless, a proper long-term average over shearing
and non-shearing states retrieves an invariant flux (and Nu) profile throughout the depth
of the atmosphere.

After appropriately time-averaging the fluxes for $\geq 200 t_b$, a sensible Nu is retrieved.  
Nusselt numbers for
all simulations at low and high Ma are plotted in Fig. \ref{fig:nu_v_ra}.  At $\epsilon = \{10^{-4}, 10^{-7}\}$,
scaling laws of $Nu \propto Nu^{\{0.31, 0.31\}}$ are retrieved.  At $\epsilon = 0.5$, in the near-sonic
regime ($Ra \leq 10^4$), the scaling of $Nu$ with $Ra$ is inflated, with $Nu \propto Ra^{0.45}$.  As simulations
pass into the supersonic regime and shocks start to form near the downflows,
that scaling drops to $Nu \propto Ra^{0.19}$.

\begin{figure}[t]
\includegraphics[width=3.4375in]{./figs/nu_v_ra.png}
\caption{Variation of Nu as Ra increases at low and high Ma. 
At high $\epsilon$ (purple circles), 
a clear transition from the subsonic to supersonic regime is evident in the scaling
of Nu with Ra.  In the low $\epsilon$ regime (green diamonds and yellow squares), 
Nu scalings collapse onto a similar line which is
\textbf{consistent with RB scalings?} \cite{johnston&doering2009}.  Error bars are determined
 by the square root of the variance of Nu with depth and indicate whether or not a solution is well-converged.
\label{fig:nu_v_ra} }
\end{figure}

@@

\subsection{acknowledgements}
EHA acknowledges the support of the University of Colorado’s George 
Ellery Hale Graduate Student Fellowship.
This work was supported by  NASA LWS grant number NNX16AC92G.  
Computations were conducted 
with support by the NASA High End Computing (HEC) Program through the NASA 
Advanced Supercomputing (NAS) Division at Ames Research Center
with allocations (GID s1647, PI Brown; GID g26133, PI Toomre).
We thank Axel Brandenburg, Mark Rast, and Jeff Oishi for many useful discussions.
